 % Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\usepackage{graphicx}
\graphicspath{ {Images/} }
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Clothes or Body Type}

% Please do not change the subtitle
\subtitle{COMP230 - Ethics Essay}

% Please put your student number in the author field
\author{1506530}

\begin{document}

\maketitle

\abstract {In mainstream game development, Objectification of the human body is a critical issue, though the exact cause this is uncertain. Three causes for this could be Body Type, Clothing and Pose. But which one is the biggest culprit for objectification? Taking the three variables into account we split them further into three levels having two extremes and in-between e.g. Almost no clothes, fully clothes and some clothes.
		\newpage
	Goal:  To determine weather or not in video games the Body Type or Amount of clothes worn effect a player’s perception of objectification on the games avatar.
		\newline
	Hypothesis: Lack of clothes is not the primarily contributor to the objectification of an avatar.
		\newline
	Hypothesis: Having a hyper sexualised body type may be the primary contributor.
		\newline
	Method: I shall be using a survey based primary research to evaluate peoples opinions on this subject. They will be closed ended questions with limited choice in answer i.e. a selection of three images will be presented to them and they must select one. These three examples will be one of the three variables used.
	\newline
	These results will be used to compare the views of men and women when choosing their avatar.}
	
\newpage

\section{Introduction}

According to Entertainment Software Association(ESA), in the USA of gaming females take up almost 48percent of the gaming community \cite{SexistGames}, so it is important to always take into consideration what they think of the avatars they have been given. Evidence suggests that a lot of designers do not take this into consideration, This is unfortunate as this approach can push away the female players and tends to lead to the sexist view that many people believe the gaming industry has. Though this is an issue that should be looked at what this survey intends on finding out is weather the female avatars "Sexist" look is based on the hypersexualised body type or the clothes that they wear.
		\newline
The Hypothesis for this research is that the lack of clothes is not the primarily contributor to the objectification or "sexualisation" of an avatar. But rather having a hyper sexualised body type may be the primary contributor. I shall be using a survey based primary research to evaluate peoples views on this. They will be closed ended questions with limited choice in answer. These examples will be following defined variables, and the results will be split into male/female base and compared for their view on sexulaised avatars.

\section{Background}

Over the recent years many papers have been looking heavily into the gender divide. They tend to point out the stereotypical female character and how they should be changed\cite{LaraPhenomenon,MirrorSexist,GenderSteriotype}. Though this does not point out the underlying issue, what is it that the gaming populous see as the cause for these conceptions? In the paper Hypersexual Avatars - Who wants them?\cite{WhowantsThem} they look into what avatars people chose when confronted with a variety of stereotyped females and females that have not been labeled as steriotyped. They also looked into hypersexualised bodies and clothing levels, though this was not looked into as much as the steriotyping. This is unfortunate as looking into how people perceive female avatars from appearance alone would have given a clearer answer on the conception of female objectification. 

\section{Method}

\subsection{Definitions}

The variables that this paper will be using to judge players perception of the female avatar will be hypersexualised and "average" bodies and the level of clothes worn for both instances of body type.
\newline
In the book Gender Inclusive Game Design\cite{Graner}, Graner describes a hypersexual body as having: unnaturally large breasts, a shapely behind, a narrow waist, in addition to this in the book Provocateur: Images for Women and Minorities in Advertising\cite{WomenAds}, young features, exaggerated leg length and visible cleavage between the buttocks and breast will also be used as standards for hypersexualisation.

The level of clothing used will be determined by the article Disco Clothing, Female Sexual Motivation and Relationship Status: Is She Dressed to Impress\cite{SkinExpose}. This sexology research indicates that women with more visible skin are typically more sexually available. For this paper clothing will be defined by more body skin shown and less to no body skin shown.

\subsection{Survey}
This paper will be using a survey based primary research to indicate the views of people on the avatars they are given to choose from. When choosing an avatar they will be forced to choose between two instances of avatars and example follows:

They will be split into male and female participants and the results will be looked at using the gender divide of male/female. This information will be used to discover the differences or similarities between male and female choices in avatars. We will be analysing the different choices that people make on weather the body type or clothing level effects the conception of their avatar.

\section{Results}

\section{Conclusion}


\bibliographystyle{ieeetr}
\bibliography{Ethics-Bib}

\end{document}
